---
title: "Final Project"
author: "Charlie Zhan_MSQF"
date: "4/29/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Finance Project: Pricing performance of factors
```{r}
rm(list = ls())
library(cbw)
```
1. Select 10 stocks that you are interested in. Find their yahoo symbols. This website can help you find the symbols that yahoo is using http://investexcel.net/all-yahoo-financestock-tickers/. Remember to double check the symbols at yahoo finance.

```{r}
symbols=c('AAPL','BAC','AMZN','T','GOOG','IBM','F','UBS','ACN','EA')
symnames=c('apple','boa','amazon','att','google','ibm','ford','ubs','accenture','ea')
```

2. Download monthly premium data for each stock from Jan 2005 to Dec 2018 using the
cbw getfinmdat() function. Remember this requires that all 10 stocks you select in step 1 should be available for this time frame.

```{r}
prmdf = getfinmdat(symbols=symbols,symnames=symnames,
                   from ="2004-12-31",
                   to = "2018-12-31")
head(prmdf)
```

3. Load the package czzg and use the data(factor12) as given to find the best factor
collection by the Chib, Zeng and Zhao (2020) method. Use a student-t distribution for the errors and let nu = 5 in the model scan.

```{r}
library(czzg)
plan(multisession)
data("factor12")
datdf = factor12
scanls  = CZZtscan(data = datdf,nu = 5)
scandf = scanls$scandf
scandford = scandf[order(scandf$logmarg,decreasing = T),]
Mst = which.max(scandf$logmarg);
scandf[Mst,];
# the best model is Mkt + SMB + ROE + PEAD + MGMT
```

4. Combine the data in factor12 with the data on the 10 stock premiums (this means that at this point you will remove all the rows in factor12 before January 2005).

```{r}
datdfn = datdf[373:540,]
prmdfn = prmdf[,1:10]
prmfactordf = cbind(datdfn,prmdfn)
```

5. Use the factors from the best model to see how many of the 10 stocks can be priced (for each stock you need to fit two models - one with an intercept and one without, as described in the which factors note).

```{r}
xnames = c("Mkt","SMB","ROE","PEAD","MGMT")
ynames = names(prmdfn)
czzfrm = "~Mkt + SMB + ROE + PEAD + MGMT"
J = length(ynames)
marglik1 = rep(0,J)
marglik0 = rep(0,J)
for (j in 1:J) {
  ynamesj = ynames[j]
  frmj = as.formula(paste(ynamesj,czzfrm,sep = ""))
  frmj0 = as.formula(paste(ynamesj,czzfrm,"-1",sep = ""))
  theta1m = MCMCregresst(modelfrm = frmj,
                         data = prmfactordf,
                         nu=5);
  theta0m = MCMCregresst(modelfrm = frmj0,
                         data = prmfactordf,
                         nu=5);
  marglik1[j] = logmarglik(theta1m);
  marglik0[j] = logmarglik(theta0m);
}
diff = marglik1 - marglik0; 
ynames[diff > 1.15]
#9 of the 10 stocks can be priced, except Apple
```

## Marketing Project: Brand complements and substitutes

```{r}
data("tuna")
dftuna=tuna
```

1. Load the tuna data set. There are seven brands in the data set. For each brand,
estimate separate independent student-t models where logsales for each product is
regressed on an intercept, the product’s log price and display activity. Use the default training sample prior and use log-marginal likelihoods to find the appropriate-degrees of freedom of the student-t distribution on the grid seq(from = 3,to = 6,length.out = 11).

```{r}
nug = seq(from = 3,to = 6,length.out = 11)
J = 7
xnames = c( "~ LPRICE", "+ NSALE")
ynames = "MOVE"
marglik = rep(0,J)
for (j in 1:J) {
  ynamesj = paste(ynames,j,sep = "")
  xnamesj= paste(xnames,j,sep = "",collapse = "")
  modelj = as.formula(paste(ynamesj,xnamesj,sep = ""))
  outlsj= mapply("MCMCregresst",
                  nu = nug,
                  MoreArgs = list(modelfrm = modelj, data = dftuna),
                  SIMPLIFY = FALSE)
  marglikj = logmarglik(outlsj);
  marglik[j]= marglikj
  A = cbind(nug,t(marglikj))
  indj = which.max(A[,2]); # which model has the largest marg lik
  colnames(A) = c("nu","logmarg")
  rnames = paste("brand",j,sep = "",collapse = "")
  rnames = rep(rnames,times = length(nug))
  rownames(A) = rnames
  print(A[indj,,drop = F])
}
```

2. Now estimate a SURE student-t model for the seven brands. Again use marginal
likelihoods to find the appropriate degrees of freedom on the grid seq(from = 3,to =6,length.out = 11).

```{r}
suremodels=list()
for (j in 1:J) {
  ynamesj = paste(ynames,j,sep = "")
  xnamesj= paste(xnames,j,sep = "",collapse = "")
  suremodels[[j]] = as.formula(paste(ynamesj,xnamesj,sep = ""))
}
sureoutls= mapply("MCMCsuret",
                nu = nug,
                MoreArgs = list(modelfrm = suremodels, data = dftuna),
                SIMPLIFY = FALSE)
suremarglik = logmarglik(sureoutls);
B = cbind(nug,t(suremarglik))
colnames(B) = c("nu","logmarg")
sureind = which.max(B[,2]); # which model has the largest marg lik
surethetatm = sureoutls[[sureind]]
print(B[sureind,,drop = F])
```
3. Do you find that the SURE-t model is an improvement over the independent t-models?

```{r}
sum(marglik)
logmarglik(surethetatm)
#Yes, because SURE-t model has greater marginal likelihood
```

4. From the best fitting SURE-t model, what brands appear to be complements and which appear to be substitutes?

```{r}
summarycorr(surethetatm)
#complements have positive correlation coefficient, while substitutes have negative correlation coefficient
#brand 3 and brand 6 have a correlation of 0.48, so this two appear to be complements.
#brand 6 and brand 7 have a correlation of -0.15, so this two appear to be complements.

```
